### 2011-01-31 trunk/papers/webist2011/paper_sec_conclusions.tex
added some more hints for future work
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@1230 d8b0c59b-6544-0410-94d9-83a5658a058e

The current version of the wrapping tool permits to create resource adapters for RESTful web services.
SOAP-based services are also experimentally supported. As potential future work, we consider to include semantically enriched WSDL documents using SAWSDL, and to support other SWS approaches such as WSMO-lite services --- however, real-life examples of these are still hard to find.

>>>>

As potential future work, we consider to include semantically enriched WSDL documents using SAWSDL, and to support other SWS approaches such as WSMO-lite services, making the web service wrapping a semi-automatic (or automatic) process. As regards to the discovery, once the catalogue begins to be populated, applying techniques such as frequent itemset mining or collaborative filtering could be an interesting way to offer better recommendations to the users.

% The current version of the wrapping tool permits to create resource adapters for RESTful web services.
% SOAP-based services are also experimentally supported. As potential future work, we consider to include semantically enriched WSDL documents using SAWSDL, and to support other SWS approaches such as WSMO-lite services --- however, real-life examples of these are still hard to find.
